Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2019-08-14 peakcharacterization_manuscript.Rmd
a draft of the abstract

>>>>

## Abstract

We introduce a novel method for characterizing peaks from direct injection FT-MS experiments developed on metabolomics datasets that utilizes calculated frequency values derived directly from the spacing of raw M/Z points. Our method incorporates several aspects designed to make the derived intensities trustworthy, and suitable for use in our previously published peak assignment algorithm SMIRFE. Notably, the inclusion of an intensity independent noise removal, and normalization of scan level data results in a reduction of median relative standard deviation from **X** to **Y**, and much better fit of peak intensities to relative natural abundances of assigned isotopologues.
